%-------------------------
% Resume in Latex
% Author : Venu Dattathreya Vemuru
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------



\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
\usepackage{helvet}  % Arial/Helvetica equivalent
\renewcommand{\familydefault}{\sfdefault}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins for one-page fit
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - tighter spacing
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands - tighter spacing
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumePublicationsHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}



\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   \textbf{\href{}}{\Large Venu Dattathreya Vemuru} & Email: \href{mailto:venudattathreya@gmail.com}{venudattathreya@gmail.com}\\
   \href{https://www.linkedin.com/in/venu-dattathreya-vemuru-a5020b225}{LinkedIn} \hspace{1em} \href{https://github.com/venu284}{GitHub} & Mobile: +1-(706)-380-2548 \\
\end{tabular*}

%----------PROFESSIONAL SUMMARY------------
%\section{Professional Summary}
%\begin{itemize}[leftmargin=0.15in, label={}]
  %  {\item{
   %  Computer Science graduate student experience in predictive modeling, machine learning algorithms, and large-scale data processing. Developing scalable ML solutions with experience in computer vision and statistical analysis. Passionate about implementing efficient algorithms for complex data challenges and collaborating across teams to deliver innovative solutions. Seeking a Machine Learning internship at Adobe to apply technical expertise in developing predictive models and optimization techniques for customer experience enhancement.
 %   }}
%\end{itemize}




%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graduate Research Assistant — Genomic Prediction of Soybean Yield}{Jan 2025 - Present}
      {University of Georgia}{Athens, GA}
      \resumeItemListStart
        \resumeItem{Engineered a scalable dimension reduction pipeline for high-dimensional DNA sequence data, implementing Gaussian Process models with distributed computing that improved prediction accuracy by 23\%.}
        \resumeItem{Developed optimized Python data preprocessing algorithms for genetic sequences, implementing NumPy vectorization that reduced processing time by 65\% while ensuring cross-dataset model performance.}
        \resumeItem{Implemented multiple dimensionality reduction techniques (PCA, t-SNE, UMAP) with scikit-learn hyperparameter tuning to identify the most efficient approach for genomic data visualization.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Graduate Research Assistant — Automated Maize Brace-Root Phenotyping}{Jan 2025 - Present}
      {University of Georgia}{Athens, GA}
      \resumeItemListStart
        \resumeItem{Designed computer vision system using PyTorch and OpenCV for agricultural phenotyping, improving maize root segmentation accuracy from 47\% to 71\% through optimization of U-Net architecture.}
        \resumeItem{Established deep learning pipeline including transfer learning and data augmentation techniques that reduced analysis time by 35\% compared to manual methods.}
        \resumeItem{Architected data processing solution with Python that resolved complex JSON annotation formats and data integrity challenges for distributed machine learning model training.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Cybersecurity Intern}{Feb 2023 - Mar 2023}
      {Corizo}{Bengaluru, India (Remote)}
      \resumeItemListStart
        \resumeItem{Identified 50+ vulnerabilities using Nmap, Burp Suite and Metasploit; implemented patches improving security by 25\% and developed automation reducing manual effort by 40\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

\resumeProjectHeading
          {\textbf{Image Caption Generator} - \emph{TensorFlow, VGG16, LSTM, Python}}{Dec 2024}
          \resumeItemListStart
            \resumeItem{Created image captioning system combining VGG16 CNN for feature extraction and LSTM networks, achieving BLEU-1 score of 0.64; processed 8,000+ images extracting 4096-dimensional vectors.}
            \resumeItem{Developed custom data generator with Keras/TensorFlow, implementing checkpoint-based training reducing model loss from 6.36 to 3.96 with 8,700+ word vocabulary.}
          \resumeItemListEnd 
      \resumeProjectHeading
          {\textbf{E-Cinema Booking System} - \emph{React, Node.js, Express, MongoDB, JWT}}{Feb 2025}
          \resumeItemListStart
            \resumeItem{Architected a comprehensive full-stack web application providing interactive digital experiences for movie browsing and booking, implementing modern UI design patterns and responsive layouts that enhanced user engagement.}
            \resumeItem{Engineered dynamic seat selection interface with client-side rendering optimizations, reducing load times by 40\% while maintaining a seamless, visually compelling user experience.}
            \resumeItem{Developed modular, reusable frontend components and backend microservices with thorough test coverage, ensuring 99.9\% uptime and 1000+ concurrent users support through clean, maintainable code and efficient algorithms.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Student Face Recognition System} - \emph{Python, Flask, React, OpenCV}}{Jan 2025}
          \resumeItemListStart
            \resumeItem{Designed and implemented a full-stack application leveraging computer vision for real-time student identification, creating an intuitive user interface with React that visualizes complex data and provides seamless user interactions.}
            \resumeItem{Built scalable microservices architecture with RESTful APIs connecting frontend experience to backend processing, implementing efficient data flow patterns and responsive feedback mechanisms.}
            \resumeItem{Containerized application using Docker with CI/CD pipeline for continuous deployment, ensuring reliable delivery of new features while maintaining 95\%+ system accuracy and intuitive user experience.}
          \resumeItemListEnd
           
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item{
     \textbf{Languages:} Python, Java, JavaScript, SQL \\
     \textbf{ML/AI:} TensorFlow, PyTorch, Scikit-Learn, Keras, NLP \\
     \textbf{Data Engineering:} NumPy, Pandas \\
     \textbf{DevOps:} Docker, CI/CD, Kubernetes \\
     %\textbf{Security:} Penetration Testing, Nmap, Burp Suite, Metasploit
    }
 \end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Georgia}{Athens, GA}
      {Master of Science in Computer Science}{Aug 2024 - May 2026 (Expected)}
    \resumeSubheading
      {RMK Engineering College}{Chennai, India}
      {Bachelor of Science in Computer Science}{Aug 2020 - May 2024}
  \resumeSubHeadingListEnd

%-----------Publications-----------
\section{Publications}
    \resumeSubHeadingListStart
      \resumePublicationsHeading
          {\textbf{IEEE ICRMKM-AI}}{Jan 2024}
          \resumeItemListStart
            \resumeItem{Vemuru, V.D., et al. \href{https://ieeexplore.ieee.org/document/10369555}{Enhancing Image Deblurring Algorithm Selection and Performance Evaluation for CCTV}.}
            \resumeItem{Vemuru, V.D., et al. \href{https://ieeexplore.ieee.org/document/10369553}{Securing Children Based on IoT and Emotion Prediction}.}
            \resumeItem{Vemuru, V.D., et al. \href{https://ieeexplore.ieee.org/document/10368901}{AI-Powered Visual Aid System for the Blind}.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}
